### 2023-11-20 chapters/paper_modelagnostic.tex
Fix notation for layer-number and timestep
Add source reference at the top of every paper chapter

\chapter[model-agnostic out-of-distribution detection using combined statistical tests]{Model-Agnostic Out-of-Distribution Detection Using Combined Statistical Tests}
\label{chp:paper-modelagnostic}
\ifthenelse{\equal{\skippapers}{true}}{}{

@@

As can be seen in \cref{fig_modelagnostic:type1}, we have that the Type I ratio line stays below the identity line, meaning that the BH correction is working. When deciding for a specific threshold $\alpha$, we usually have to trade off between Type I and Type II error and in most cases the threshold to choose depends on the application domain. Ideally, we would like to have a low Type I and a low Type II error rate, meaning that we are not considering a lot of in-distribution examples as OOD and at the same time considering a lot of outliers as in-distribution. \cref{fig_modelagnostic:type1} shows that we can achieve this for low values of $\alpha$. When training on CIFAR, instead, we are able to control the FDR only from a certain significance level (see \cref{appendix_modelagnostic:BH_cifar}). This is expected given that the AUROC is not as good as when testing on MNIST.

>>>>

\chapter[model-agnostic out-of-distribution detection using combined statistical tests]{Model-Agnostic Out-of-Distribution Detection Using Combined Statistical Tests}
\label{chp:paper-modelagnostic}

\textit{This chapter is a piece of original research published as part of the project:} \newline
\begin{center}
    \begin{enumerate}[leftmargin=8mm,rightmargin=8mm,topsep=0mm,label={[\Alph*]}]
        \setcounter{enumi}{1}
        \item \fullcite{bergamin_modelagnostic_2022} \co \label{enumerate: paper-modelagnostic}
        \end{enumerate}
\end{center}

\ifthenelse{\equal{\skippapers}{true}}{}{

@@

As can be seen in \cref{fig_modelagnostic:type1}, we have that the Type I ratio line stays below the identity line, meaning that the BH correction is working. When deciding for a specific threshold $\alpha$, we usually have to trade off between Type I and Type II error and in most cases the threshold to choose depends on the application domain. Ideally, we would like to have a low Type I and a low Type II error rate, meaning that we are not considering a lot of in-distribution examples as OOD and at the same time considering a lot of outliers as in-distribution. \Cref{fig_modelagnostic:type1} shows that we can achieve this for low values of $\alpha$. When training on CIFAR, instead, we are able to control the FDR only from a certain significance level (see \cref{appendix_modelagnostic:BH_cifar}). This is expected given that the AUROC is not as good as when testing on MNIST.
